From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-17 paper.tex
Minor change to make the 'matches' picture more readble

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\columnwidth]{experimental_setup}
    \caption{\small \textbf{Experimental setting}. The areas of interest (AOI)
    considered of potential focuses of attention are circled in red.}
    \label{drawSetup}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{matches}
    \caption{\small \textbf{Comparison of computed focus of attention \vs ground
        truth} during a 20+ min face-to-face child-robot interaction.
        In orange (top line), the focus of attention as computed by the robot;
        in blue (bottom line), the focus of attention as manually annotated. The
    bottom graph shows agreements.}

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\columnwidth]{experimental_setup}
    \caption{\small \textbf{Experimental setting}. The areas of interest (AOI)
    of potential focuses of attention are circled in red.}
    \label{drawSetup}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{matches}
    \caption{\small \textbf{Comparison of computed focus of attention \vs ground
        truth} during a 20+ min face-to-face child-robot interaction (subject 4
        in table~\ref{tab:results}).
        In blue (top line), the focus of attention as computed by the robot;
        in orange (bottom line), the focus of attention as manually annotated
        (ground truth). The bottom graph shows agreements.}
